---
title: "Fileado Website Analytics Dashboard"
output: 
  flexdashboard::flex_dashboard:
    orientation: columns
    vertical_layout: fill
---

```{r setup, include=FALSE}
library(flexdashboard)
library(ggplot2)
library(plotly)
library(DT)
library(reshape2)
library(ggpubr)
library(plyr)
library(dplyr)
source("data_clean.R")
source("data_aggregate.R")
```

# Overview

## Column {data-width=400, .tabset}

### Daily Visits

```{r}
chart_daily_visits = ggplot(melt(daily_visits,id.vars="Date", value.name="Visits", variable.name="Type"), aes(x=Date, y=Visits, group=Type, color=Type)) +
    geom_line(size=1)+
    ylim(0,round_any(max(daily_visits$`Total Visits`)+10,10))+
    theme_pubclean()

ggplotly(chart_daily_visits)
```

### Weekly Visits

```{r}
chart_weekly_visits = ggplot(melt(weekly_visits,id.vars="Week", value.name="Visits", variable.name="Type"), aes(fill=Type, x=Week, y=Visits)) +
  geom_bar(position="dodge", stat="identity", width=0.6)+
  theme_pubclean()

ggplotly(chart_weekly_visits)
```

### Monthly Visits 

```{r}
chart_monthly_visits = ggplot(melt(monthly_visits,id.vars="Month", value.name="Visits", variable.name="Type"), aes(fill=Type, x=Month, y=Visits)) +
  geom_bar(position="dodge", stat="identity", width=0.6)+
  theme_pubclean()

ggplotly(chart_monthly_visits)
```

### Yearly Visits

```{r}
chart_yearly_visits = ggplot(melt(yearly_visits,id.vars="Year", value.name="Visits", variable.name="Type"), aes(fill=Type, x=Year, y=Visits)) +
  geom_bar(position="dodge", stat="identity", width=0.6) +
  scale_x_continuous(breaks=c(2019,2020,2021,2022,2023,2024,2025))+
  theme_pubclean()

ggplotly(chart_yearly_visits)
```

## Column {data-width=400, .tabset}

### Weekly Total Visits by Sections

```{r}
chart_weekly_page_visits = ggplot(weekly_page_visits[,c(1,2,3)], aes(fill=Section, y=`Total Visits`, x=Week)) + 
    geom_bar(position="stack", stat="identity", width=0.6)+
    theme_pubclean()

ggplotly(chart_weekly_page_visits)
```

### Monthly Total Visits by Sections

```{r}
chart_monthly_page_visits = ggplot(monthly_page_visits[,c(1,2,3)], aes(fill=Section, y=`Total Visits`, x=Month)) + 
    geom_bar(position="stack", stat="identity", width=0.6)+
    theme_pubclean()

ggplotly(chart_monthly_page_visits)
```

### Yearly Total Visits by Sections

```{r}
chart_yearly_page_visits = ggplot(yearly_page_visits[,c(1,2,3)], aes(fill=Section, y=`Total Visits`, x=Year)) + 
    geom_bar(position="stack", stat="identity", width=0.6)+
    scale_x_continuous(breaks=c(2019,2020,2021,2022,2023,2024,2025))+
    theme_pubclean()

ggplotly(chart_yearly_page_visits)
```

## Column {data-width=200}

### Page Visits per Session

```{r}
chart_visits_per_session = pages_per_visit %>%
  arrange(Sessions) %>%  
  mutate(Pages=factor(Pages, levels=Pages)) %>%  
  ggplot(aes(x=Pages, y=Sessions)) + 
  geom_bar(stat = "identity", color="#00BFC4", fill="#00BFC4", width=0.6, gap=0.5) +
  coord_flip()+
  theme_classic()

ggplotly(chart_visits_per_session)
```

### Drop-off Sections

```{r}
chart_drops = drop_off_section %>%
  arrange(Drops) %>%  
  mutate(Page=factor(Page, levels=Page)) %>%  
  ggplot(aes(x=Page, y=Drops)) + 
  geom_bar(stat = "identity", color="#F8766D", fill="#F8766D", width=0.6, gap=0.5) +
  coord_flip()+
  theme_classic()

ggplotly(chart_drops)
```

# Blog Section

## Column {data-width=500}

### Total Article Visits

<style>
.dataTables_scrollBody {
    max-height: 100% !important;
}
</style>

```{r}
datatable(article_visits, extensions = 'Buttons', options = list(
  dom = 'Blfrtip',
  pageLength = 25,
  buttons = c('copy', 'print', 'csv')))
```

## Column {data-width=500}

### Most Popular Authors by Total Visits Share

```{r}
plot_ly(data=author_visits[,c(1,2)],labels=~ID, values=~`Total Visits`) %>% add_pie(hole = 0.5) %>%
        layout(title = '',
           xaxis = list(showgrid = FALSE, zeroline = FALSE, showticklabels = FALSE),
           yaxis = list(showgrid = FALSE, zeroline = FALSE, showticklabels = FALSE))
```

### Author Popularity Over Time (Weekly Basis)

```{r}
author_visits_time = author_visits_time[,c(1,2,3)] %>%
  ggplot( aes(x=Week, y=`Total Visits`, group=ID, color=ID)) +
    geom_line(size=1)+
    ylim(0,round_any(max(author_visits_time$`Total Visits`)+10,10))+
    theme_pubclean()

ggplotly(author_visits_time)
```
